---
title: "module1 "
output: html_document
---

```{r}

fev1 <- c(
  Patient_01 = 85,
  Patient_02 = 62,
  Patient_03 = 45,
  Patient_04 = 91,
  Patient_05 = 38,
  Patient_06 = 70,
  Patient_07 = 55,
  Patient_08 = 76,
  Patient_09 = 49,
  Patient_10 = 88
)

age <- c( 
  Patient_01 = 23, 
  Patient_02 = 67, 
  Patient_03 = 41, 
  Patient_04 = 58, 
  Patient_05 = 34, 
  Patient_06 = 72, 
  Patient_07 = 29, 
  Patient_08 = 46, 
  Patient_09 = 81, 
  Patient_10 = 19 
)
```

How many patients are younger than 40?

```{r}

sum(age < 40)

sum((age>25) &(40 <= fev1) & (fev1<=70))

sum((age%%2==0) & (fev1%%2!=0))

id<- fev1[fev1<70]
print(id)

```

Write a series of expressions that categorize Patient 02's FEV1 as:
"Healthy" if FEV1 is greater than 80 
"Moderate impairment" if FEV1 between 60 and 80 
"Poor" if FEV1 is between 40 and 60 
"Very poor" if FEV1 is less than 40
```{r}
 p2 <- fev1 ["Patient_02"]

if(p2 > 80){
  print("Healthy")
}else if((80 > p2) & ( p2>60)){
  print("Moderate impairment")
}else if((60>p2)& (p2>40)){
  print("Poor")
}else{
  print("Very poor")
}


```
Go through every patient’s FEV1 and print:
"Healthy" if FEV1 is greater than 80 
"Moderate impairment" if FEV1 between 60 and 80 
"Poor" if FEV1 is between 40 and 60 
"Very poor" if FEV1 is less than 40


Now modify the loop to print something like:Patient_01: HealthyPatient_02: Moderate

```{r}

for( p in names(fev1)){
  if( fev1[p] > 80){
  print(paste0( p,":Healthy"))
  }else if( fev1[p] >60){
  print(paste0( p,":Moderate impairment"))
  }else if(fev1[p]>40){
  print(paste0( p,":Poor"))
  }else{
  print(paste0( p,":Very poor"))
}}



```
```{r}

over_3_vec <- c()
for(patientid in names(age)){
}

for(patientid in names(age)){
  print(paste(patientid,age[patientid]))
  if(age[patientid] >30){
    print("Over 30")
  }
  else{
    print("under 30")
  }
  
}

```
Write a for loop that:
Prints the age and FEV1 of each participant 
Keeps a running total of participant ages 
Stops the loop once the cumulative age exceeds 150 

```{r}
cumi_age<-0
for(id in names(fev1)){
  print(paste(id,":","age=",age[id],"FEV1=",fev1[id]))
  cumi_age <- cumi_age + age[id]
if(cumi_age>150){
  break
}
}

```